\chapter{Configurations}\label{configurations}

\section{Introduction}\label{introduction-1}

The Roa Logic AHB-Lite APB4
Bridge is a fully configurable bridge IP to enable AHB-Lite based hosts
to communicate with APB4 based peripherals. The core parameters and
configuration options are described in this section.

\section{Core Parameters}\label{core-parameters}

\begin{longtable}[]{@{}lccl@{}}
	\toprule
	Parameter & Type & Default & Description\tabularnewline
	\midrule
	\endhead
	\texttt{HADDR\_SIZE} & Integer & 32 & AHB-Lite Address Bus Size\tabularnewline
	\texttt{HDATA\_SIZE} & Integer & 32 & AHB-Lite Data Bus Size\tabularnewline
	\texttt{PADDR\_SIZE} & Integer & 10 & APB4 Address Bus Size\tabularnewline
	\texttt{PDATA\_SIZE} & Integer & 8  & APB4 Data Bus Size\tabularnewline
	\texttt{SYNC\_DEPTH} & Integer & 3  & Clock Domain Crossing Sync
	Stages\tabularnewline
	\bottomrule
	\caption{Core Parameters}
\end{longtable}

\subsection{HADDR\_SIZE}\label{haddr_size}

The \texttt{HADDR\_SIZE} parameter specifies the width of the address bus for the
AHB-Lite interface.

\subsection{HDATA\_SIZE}\label{hdata_size}

The \texttt{HDATA\_SIZE} parameter specifies the width of the data bus for the
AHB-Lite interface. This parameter must equal an integer multiple of
bytes and also be greater or equal to \texttt{PDATA\_SIZE}:

\begin{longtable}[]{@{}|rp{12cm}@{}}
	\textbf{Conditions}: & \\
	\endhead
	1. & \texttt{HDATA\_SIZE} $\geqslant$ \texttt{PDATA\_SIZE}\\
	2. & \texttt{HDATA\_SIZE MOD 8 = 0}\\
\end{longtable}	            

\subsection{PADDR\_SIZE}\label{paddr_size}

The \texttt{PADDR\_SIZE} parameter specifies the width of the address bus for the
APB4 (i.e. peripheral) interface.

\subsection{PDATA\_SIZE}\label{pdata_size}

The \texttt{PDATA\_SIZE} parameter specifies the width of the data bus for APB4
(i.e. peripheral) interface. This parameter must equal an integer
multiple of bytes and also be less than or equal to \texttt{HDATA\_SIZE}.

\begin{longtable}[]{@{}|rp{12cm}@{}}
	\textbf{Conditions}: &  \\
	\endhead
	1. & \texttt{PDATA\_SIZE} $\leqslant$ \texttt{HDATA\_SIZE}\\
	2. & \texttt{PDATA\_SIZE MOD 8 = 0}\\
\end{longtable}	

\subsection{SYNC\_DEPTH}\label{sync_depth}

The APB4 Bridge IP supports operating the AHB-Lite and APB4 interfaces
in separate, unrelated clock domains. The IP automatically handles
cross-domain synchronization and the \texttt{SYNC\_DEPTH} parameter determines
the number of synchronization stages between these clock domains.

Increasing this parameter reduces the possibility of metastability for
signals crossing between the two domains, but at the cost of increased
latency.

The minimum and default value of the \texttt{SYNC\_DEPTH} parameter is 3.

\subsection{Limits to APB4 Address \& Data Sizes} \label{limits-to-apb4-address-data-sizes}

The \emph{AMBA APB v2.0 Protocol} specification limits the widths of
both Address (\texttt{PADDR\_SIZE}) and Data (\texttt{PDATA\_SIZE}) buses to 32 bits.
However the AHB-Lite APB4 Bridge IP Address and Data sizes are
\emph{not} similarly constrained -- any Address width and any
byte-aligned Data width is supported by the IP.