\section{AHB-Lite Interface}

The AHB-Lite interface is a regular AHB-Lite slave port. All signals are
supported. See the
\emph{\href{https://www.arm.com/products/system-ip/amba-specifications}{AMBA
3 AHB-Lite Specification}} for a complete description of the signals.

\begin{longtable}[c]{@{\extracolsep{\fill}}cccl@{}}	
	\toprule 
	\textbf{Port} & \textbf{Size} & \textbf{Direction} & \textbf{Description}\\
	\midrule
	\endhead 
	\texttt{HRESETn}   & 1                    & Input  & Asynchronous active low reset\\
	\texttt{HCLK}      & 1                    & Input  & Clock Input\\
	\texttt{HSEL}      & 1                    & Input  & Bus Select\\
	\texttt{HTRANS}    & 2                    & Input  & Transfer Type\\
	\texttt{HADDR}     & \texttt{HADDR\_SIZE} & Input  & Address Bus\\
	\texttt{HWDATA}    & \texttt{HDATA\_SIZE} & Input  & Write Data Bus\\
	\texttt{HRDATA}    & \texttt{HDATA\_SIZE} & Output & Read Data Bus\\
	\texttt{HWRITE}    & 1                    & Input  & Write Select\\
	\texttt{HSIZE}     & 3                    & Input  & Transfer Size\\
	\texttt{HBURST}    & 3                    & Input  & Transfer Burst Size\\
	\texttt{HPROT}     & 4                    & Input  & Transfer Protection Level\\
	\texttt{HREADYOUT} & 1                    & Output & Transfer Ready Output\\
	\texttt{HREADY}    & 1                    & Input  & Transfer Ready Input\\
	\texttt{HRESP}     & 1                    & Output & Transfer Response\\
	\bottomrule 	
	\caption{PLIC Interface Signals}
	\label{tab:AHBIF}
\end{longtable}

\subsection{HRESETn}

When the active low asynchronous \texttt{HRESETn} input is asserted
(`0'), the interface is put into its initial reset state.

\subsection{HCLK}

\texttt{HCLK} is the interface system clock. All internal logic for the
AHB-Lite interface operates at the rising edge of this system clock and
AHB bus timings are related to the rising edge of \texttt{HCLK}.

\subsection{HSEL}

The AHB-Lite interface only responds to other signals on its bus -- with
the exception of the global asynchronous reset signal \texttt{HRESETn}
-- when \texttt{HSEL} is asserted (`1'). When \texttt{HSEL} is negated
(`0') the interface considers the bus \texttt{IDLE}.

\subsection{HTRANS}

HTRANS indicates the type of the current transfer as shown in Table \ref{tab:HTRANS}

\begin{longtable}[c]{@{\extracolsep{\fill}}ccp{7cm}}	
	\toprule 
	\textbf{\texttt{HTRANS}} & \textbf{Type} & \textbf{Description}\\
	\midrule
	\endhead 
	\texttt{00} & \texttt{IDLE}   & No transfer required\\
	\texttt{01} & \texttt{BUSY}   & Connected master is not ready to accept data, but intents to continue the current burst.\\
	\texttt{10} & \texttt{NONSEQ} & First transfer of a burst or a single transfer\\
	\texttt{11} & \texttt{SEQ}    & Remaining transfers of a burst\\
	\bottomrule 	
	\caption{HTRANS Signal Types}
	\label{tab:HTRANS}
\end{longtable}

\subsection{HADDR}

\texttt{HADDR} is the address bus. Its size is determined by the
\texttt{HADDR\_SIZE} parameter and is driven to the connected
peripheral.

\subsection{HWDATA}

\texttt{HWDATA} is the write data bus. Its size is determined by the
\texttt{HDATA\_SIZE} parameter and is driven to the connected
peripheral.

\subsection{HRDATA}

\texttt{HRDATA} is the read data bus. Its size is determined by the
\texttt{HDATA\_SIZE} parameter and is sourced by the connected
peripheral.

\subsection{HWRITE}

\texttt{HWRITE} is the read/write signal. \texttt{HWRITE} asserted (`1')
indicates a write transfer.

\subsection{HSIZE}

\texttt{HSIZE} indicates the size of the current transfer as shown in table \ref{tab:HSIZE}:

\begin{longtable}[c]{@{\extracolsep{\fill}}ccl}	
	\toprule 
	\textbf{\texttt{HSIZE}} & \textbf{Size} & \textbf{Description}\\
	\midrule
	\endhead 
	\texttt{000} & 8 bit    & Byte\\
	\texttt{001} & 16 bit   & Half Word\\
	\texttt{010} & 32 bit   & Word\\
	\texttt{011} & 64 bits  & Double Word\\
	\texttt{100} & 128 bit  &\\
	\texttt{101} & 256 bit  &\\
	\texttt{110} & 512 bit  &\\
	\texttt{111} & 1024 bit &\\
	\bottomrule 	
	\caption{HSIZE Values}
	\label{tab:HSIZE}
\end{longtable}

\subsection{HBURST}

HBURST indicates the transaction burst type -- a single transfer or part
of a burst.

\begin{longtable}[c]{@{\extracolsep{\fill}}ccl}	
	\toprule 
	\textbf{\texttt{HBURST}} & \textbf{Type} & \textbf{Description}\\
	\midrule
	\endhead 
	\texttt{000} & \texttt{SINGLE} & Single access**\\
	\texttt{001} & \texttt{INCR}   & Continuous incremental burst\\
	\texttt{010} & \texttt{WRAP4}  & 4-beat wrapping burst\\
	\texttt{011} & \texttt{INCR4}  & 4-beat incrementing burst\\
	\texttt{100} & \texttt{WRAP8}  & 8-beat wrapping burst\\
	\texttt{101} & \texttt{INCR8}  & 8-beat incrementing burst\\
	\texttt{110} & \texttt{WRAP16} & 16-beat wrapping burst\\
	\texttt{111} & \texttt{INCR16} & 16-beat incrementing burst\\
	\bottomrule 	
	\caption{HBURST Types}
	\label{tab:HBURST}
\end{longtable}

\subsection{HPROT}

The \texttt{HPROT} signals provide additional information about the bus
transfer and are intended to implement a level of protection.

\begin{longtable}[c]{@{}ccl}	
	\toprule 
	\textbf{Bit\#} & \textbf{Value} & \textbf{Description}\\
	\midrule
	\endhead 
	3 & 1 & Cacheable region addressed\\
	  & 0 & Non-cacheable region addressed\\
	2 & 1 & Bufferable\\
	  & 0 & Non-bufferable\\
	1 & 1 & Privileged Access\\
	  & 0 & User Access\\
	0 & 1 & Data Access\\
	  & 0 & Opcode fetch\\
	\bottomrule 	
	\caption{HPROT Indicators}
	\label{tab:HPROT}
\end{longtable}


\subsection{HREADYOUT}

\texttt{HREADYOUT} indicates that the current transfer has finished.
Note, for the AHB-Lite PLIC this signal is constantly asserted as the
core is always ready for data access.

\subsection{HREADY}

\texttt{HREADY} indicates whether or not the addressed peripheral is
ready to transfer data. When \texttt{HREADY} is negated (`0') the
peripheral is not ready, forcing wait states. When \texttt{HREADY} is
asserted (`1') the peripheral is ready and the transfer completed.

\subsection{HRESP}

\texttt{HRESP} is the instruction transfer response and indicates OKAY
(`0') or ERROR (`1').